---
title: "Step 2, Notebook 2: Assembling Fragment data"
output: html_notebook
---
This notebook takes raw data and fits results, and cleans results for further analysis. 
It contains the second step of this pipeline. 
Specifically:
- clean results
  - isolate just paper 1 relevant compounds
  - ensure tma1 and tma2 are correctly grouped

Perform in previous notebook Exo0879--clean_and_fit.Rmd:
- Pooled all data
- Performed fitting analysis

To be performed by later notebooks:
- establish cutoffs for "bad" fits and "bad" curves, and remove them 
- Make plots
- Make tables
- Calculate relevant statistics

```{r}
library(tidyverse)

convert_numerics <- function( vec ) {
  
            if(all(varhandle::check.numeric(vec))){
                # convert the vector to numeric
                vec <- as.numeric(vec)
            }
            vec
        }

get_upper_whisker <- function(IQR_coef = 1.5, quant_col) {
  IQR_val <- stats::IQR({{quant_col}}) # <- (quantile({{quant_col}}, probs = 0.75) - quantile({{quant_col}}, probs = 0.25))
  top_hinge <- quantile({{quant_col}}, probs = 0.75)
  
  top_hinge + IQR_coef * IQR_val
}


# well is unique here! use that
merge_elements <- function( in_list ) { # this runction could use some work to be more flexible
  
   df_list <- c("tm_models_all", "df_BIC", "model")
    model_list <- c("s1_list", "s1_d_list", "s2_list", "s2_d_list")
  
  out <- list()
  
  for (df_element in df_list) {

    int <- lapply(model_list, function(x) { in_list$fits[[x]][[df_element]] %>%
                                            mutate(x, which_model = x)})  %>%
          # lapply( . , function(x) { mutate(x, which_model = model_list)} ) %>%
              bind_rows() # bind together extracted df_element from all four models

    out <- list(out, int) # add that df_element to a list
    
  }

 dRFU_tmas  <- lapply(model_list, function(x) in_list$fits[["df_tms"]]) %>%
                bind_rows() %>%
                mutate(which_model = "dRFU") %>%
                rename(mean_tma1 = "dRFU_tma") %>%
                select(well, which_model, condition, mean_tma1)

 #df_resids <- out[[3]]

out_list <- list("model_tmas" = out[[1]][[1]][[2]],
                 "model_results" = out[[2]],
                 "resid" = out[[2]] %>% select(variable, which_model, resids) %>% unnest( cols = c(resids) ),
                 "dRFU_tmas" = dRFU_tmas,
                 "df_BIC" = out[[1]][[2]] )

}

# take whichever one is closer to the s1 tma and set it as tma1
sort_tmas <- function(test_tma, anchor_tma) {
  ensure_unique <- runif(1, min = 0.001, max = 0.01)
### needs NA and error handling prior to use in dsfworld
 raw <-  if_else(abs({{test_tma}} - {{anchor_tma}}) == min(abs({{test_tma}} - {{anchor_tma}})),
            true = "new_tma1",
            false = "new_tma2")

}
```

Create raincloud plot theme
```{r}
# https://micahallen.org/2018/03/15/introducing-raincloud-plots/
library(PupillometryR) # has geom_flat_violin

raincloud_theme = theme(  # set publication-quality text sizes
                          text = element_text(size = 14),
                          
                          plot.title = element_text(lineheight=.8, face="bold", size = 16),
                          axis.title.x = element_text(size = 16),
                          axis.title.y = element_text(size = 16),
                          
                          axis.text = element_text(size = 14),
                          #axis.text.x = element_text(angle = 90, vjust = 0.5),
                          
                          # lenengd aesthetics (new feautres for legen aesthetics are available!)
                          legend.title=element_text(size=16),
                          legend.text=element_text(size=16),
                          legend.position = "right",

                          # remove gridlines; they don't add much to violin plots
                          panel.grid.minor = element_blank(),
                          panel.grid.major = element_blank(),
                          
                          # make whitespace transparent
                          panel.background = element_rect(fill = "transparent",colour = NA),
                          plot.background = element_rect(fill = "transparent",colour = NA)
                          )
```

Read in files
```{r}
###### Tidy raw data  ----------
all_processed <- readRDS("analyzed/Exp0879--20200912_all_analyzed_results.rds") # all analysis results
dfs_protein_EBPS <- readRDS("analyzed/Exp0879--20200912_all_dfs_list_no_empties.rds") # all raw data
dfs_protein_TAMRA <- readRDS("analyzed/Exp0879--20200912_all_dfs_as_input_to_analysis.rds") # no EBPs and TAMRA only, fed directly to fitting function

###### Paper 1 relevant compounds  ----------
paper1_cmpds_table <- readxl::read_excel("Exp0879--20200912_fragments_for_paper1.xlsx")

###### Untidy analysis results  ----------

```

Tidy analysis results
```{r}
#### list of experiments with results tidies
results_extracted <- lapply(all_processed, merge_elements)
```

Extract and pool residuals
```{r}
all_resids <- lapply(results_extracted, `[[`,  j = "resid" ) %>%
               bind_rows() %>%
               separate(variable, into = c("well", "channel", "plate_number"), remove = FALSE)

sum_resids <- all_resids %>%
              unite(plate_number_model, c(plate_number, which_model), remove = FALSE) %>%
              #filter(which_model == "s2_list") %>%
              group_by(which_model) %>%
              mutate(sum_abs_resid = sum(abs(resid))) %>%
              select(plate_number_model, which_model, variable, plate_number, sum_abs_resid) %>%
              ungroup() %>%
              distinct() %>%
              rename(value = sum_abs_resid) %>%

              group_by(plate_number) %>%
               mutate( outlier = if_else(value > get_upper_whisker(IQR_coef = 1.5, quant_col = value), # identify outliers
                                   true = "Rejected",
                                   false = "Retained") )

sum_resid_rejects <- sum_resids$variable %>% unique()
```

TO DO: Isolate Paper 1 relevant info
```{r}
all_model_tmas
```


Isolate data for all paper 1 componds 
Extract compound/layout information from the original dataframges
```{r}
###### Create a tibble containing all information for the paper 1 compounds + ADPribose + DMSO
## Extract and bind the model results from all experiments
all_model_tmas <- lapply(results_extracted, `[[`,  j = "model_tmas" ) %>%
                  bind_rows()
##### Handle the cases where there is a ZINC column but no compound column
#has_compound_conc_col <-  map( dfs_protein_TAMRA , ~"compound_conc" %in% names(.x)  ) %>% as_vector()

# Identify tibbles with ZINC but no compound columns
has_ZINC_col <- map( dfs_protein_TAMRA , ~"ZINC" %in% names(.x)  ) %>% as_vector() # has ZINC
missing_compound_col <- map(dfs_protein_TAMRA , ~!"compound" %in% names(.x)  ) %>% as_vector() # doesn't have compound

has_ZINC_col_only <-  map2( has_ZINC_col, missing_compound_col, all) %>% as_vector() # has ZINC and no compound

# Bind tube label information to the tibbles with a compound column
with_compound_col <- dfs_protein_TAMRA[!has_ZINC_col_only] %>%  
                    map(. , ~left_join(.x, paper1_cmpds_table))

# Isolate the ZINC-only tibbles and add the compound names
with_compound_col <- dfs_protein_TAMRA %>% 
                      .[has_ZINC_col_only] %>%
                       map(. , ~left_join(.x, paper1_cmpds_table)) %>%
                      c(. , with_compound_col ) # re-combine with the tibbles which already had compound cols

# only keep tibbles which note compound concentration
has_compound_conc_col <- map( with_compound_col , ~"compound_conc" %in% names(.x)  ) %>% as_vector()

###### All raw data for all paper-1 compounds --------------
all_raw <- with_compound_col %>%
                      .[has_compound_conc_col] %>%
                      map(. , ~select(.x, c(condition, plate_number, compound, compound_conc, xtal_hit, batch, Temperature, value, value_norm, paper_1 )) ) %>%
                      map(. , ~mutate_all(.x, as.character)) %>%
                      bind_rows( )  %>%
                      ungroup( )%>%
                      mutate_all( . ,convert_numerics) %>% # this misses the compond conc column--is it because of decimal places??
                      mutate_at( . ,"compound_conc", as.numeric) %>%
                      filter(is.na(compound) == FALSE,
                             !compound %in% c("Empty", "None", "ATP", "ADP", "6511", "8637", "9020")) %>%
                      mutate(compound = recode(compound,  adp_rib_control = "ADPribose", ADPriibose = "ADPribose")) %>%
                      mutate(compound =  str_remove( compound , "^0+")) %>%  # remove leading zeroes to merge these two forms of indexing
                      mutate(variable = condition)

all_raw$compound %>% unique() %>% length() 
# [1] 134

paper1_raw <- all_raw %>% filter(paper_1 == "Yes")
paper1_raw$compound %>% unique() %>% length()
# [1] 59 # including DMSO and ADPribose

###### All layouts for all paper-1 compounds --------------
all_layouts <- all_raw %>% 
                  select(condition, variable, plate_number, compound, compound_conc, xtal_hit, batch, paper_1) %>%
                  distinct()

all_layouts$compound %>% unique() %>% length()
# [1] 134

paper1_layouts <- paper1_raw <- all_layouts %>% filter(paper_1 == "Yes")
paper1_layouts$compound %>% unique() %>% length()
# [1] 59 # including DMSO and ADPribose

paper1_layouts %>% head()

###### All Tmas for all paper 1 compounds, correctly sorted --------------
## Extract and bind the model results from all experiments
all_tmas <- lapply(results_extracted, `[[`,  j = "model_tmas" ) %>%
                  bind_rows() %>%
                  ungroup() %>%
                  mutate(variable = condition) %>%
                  select(condition, variable, mean_tma1, mean_tma2, which_model) %>%
                  rename(tma1 = "mean_tma1", tma2 = "mean_tma2") %>%

                  pivot_wider(names_from = which_model, values_from = c(tma1, tma2)) %>%


                  pivot_longer(cols = c("tma1_s2_list", "tma2_s2_list",
                                        "tma1_s2_d_list", "tma2_s2_d_list"), names_to = "model_and_tma") %>%
                  filter(is.na(value) == FALSE) %>%
                  mutate(which_tma = str_sub(model_and_tma, start = 0, end = 4),
                         two_sig_model = str_sub(model_and_tma, start = 6, end = -1)) %>%
                  ungroup() %>%
                  mutate(value = value + runif( n = nrow(.),  min = 0.001, max = 0.01)) %>% # a little hack to ensure uniqueness
                  group_by(variable, two_sig_model) %>%

                  mutate(closest_to_tma1 = sort_tmas(value, tma1_s1_d_list)) %>%
                  select(-c(model_and_tma, which_tma))  %>%
                  pivot_wider(names_from = closest_to_tma1, values_from = value) %>%
                  pivot_wider(names_from = two_sig_model, values_from = c(new_tma1, new_tma2))  %>%
                  rename_with( ~gsub( pattern = "new_", replacement = "", .x), starts_with("new_")) %>%
                  pivot_longer(cols = c("tma1_s1_list",   "tma2_s1_list",
                                        "tma1_s1_d_list", "tma2_s1_d_list",
                                        "tma1_s2_list",   "tma2_s2_list",
                                        "tma1_s2_d_list", "tma2_s2_d_list"), names_to = "model_and_tma") %>%
                  mutate(which_tma = str_sub(model_and_tma, start = 0, end = 4),
                         which_model = str_sub(model_and_tma, start = 6, end = -1)) %>%
                  select(-model_and_tma) %>%
                  pivot_wider(names_from = which_tma, values_from = value) %>%
                  left_join(all_layouts) %>%
                  filter(is.na(compound) == FALSE)
                  
                  all_tmas %>% head()
 
all_model_tmas$compound %>% unique() %>% length()
# [1] 134

all_model_tmas$compound %>% unique() %>% length()

paper1_tmas <- all_tmas %>% filter(paper_1 == "Yes")
paper1_tmas$compound %>% unique() %>% length()
# [1] 59

```

```{r}
##### Just the DRC experiments
paper1_tma_DRCs_2 <- all_tmas %>%
                    #filter(plate_number %in% c("Exp0868", "Exp0877_plate3", "Exp0877_plate4")) %>%
                    filter(which_model == "s2_list") %>%
                    #filter(plate_number %in% c("Exp0868", "Exp0877_plate3", "Exp0877_plate4")) %>%
                    unite(condition, c(compound, compound_conc), remove = FALSE) %>%
                    group_by(condition) %>%
                    mutate(mean_tma1 = mean(tma1),
                           sd_tma1   = sd(tma1),
                           mean_tma2 = mean(tma2),
                           sd_tma2   = sd(tma2)) 

paper1_tma_DRCs_2$plate_number %>% unique()
all_tmas$plate_number%>% unique()

paper1_tma_DRCs_2 %>% 
  filter(compound == "DMSO") %>%
  select(-c(mean_tma1, sd_tma1, mean_tma2, sd_tma2)) %>%
  ungroup() %>%
  group_by( condition, plate_number) %>%
                      mutate(mean_tma1 = mean(tma1),
                           sd_tma1   = sd(tma1),
                           mean_tma2 = mean(tma2),
                           sd_tma2   = sd(tma2)) %>%
  select(plate_number:condition, mean_tma1:sd_tma2) %>%
  distinct()

  
```


START A NEW NOTEBOOK FOR THESE RAW DATA PLOTS IN THE END
Isolate and plot just the DRCs from the last three experiments
```{r}
##### Just the DRC experiments
paper1_tma_DRCs <- paper1_tmas %>%
                    filter(plate_number %in% c("Exp0868", "Exp0877_plate3", "Exp0877_plate4")) %>%
                    filter(which_model == "s2_list") %>%
                    #filter(plate_number %in% c("Exp0868", "Exp0877_plate3", "Exp0877_plate4")) %>%
                    unite(condition, c(compound, compound_conc), remove = FALSE) %>%
                    group_by(condition) %>%
                    mutate(mean_tma1 = mean(tma1),
                           sd_tma1   = sd(tma1),
                           mean_tma2 = mean(tma2),
                           sd_tma2   = sd(tma2)) 


p_tma_init <- paper1_tma_DRCs %>%
  ungroup() %>%
  filter(which_model == "s2_list") %>%
ggplot( aes(color = xtal_hit)) +
 # geom_point(aes(x = compound_conc, y = tma1), alpha = 1, size = 1) +
  #ylim(c(49, 55)) +
  #geom_linerange(aes(ymin = `Tma 1`  -tma1, ymax = tma1  + tma1_sd)) +
  facet_wrap(~compound, scales = "free") +
  scale_x_continuous(trans = "log2") +
  labs( x = "[Compound] (µM)", y = "Tma of major transtion (Model 3)", title = "Nsp3 Mac1 Fragments, Batch 1") 

p_tma_raw <- p_tma_init +   geom_point(aes(x = compound_conc, y = tma1), alpha = 0.8)
ggsave("draft_figures/Exp0879--20200914_tma_DRCs_model3_fixed_2.pdf", p_tma_raw, width = 15, height = 15)

p_tma_mean <- p_tma_init +geom_point(aes(x = compound_conc, y = mean_tma1), alpha = 0.8) +
  geom_linerange(aes(x = compound_conc, ymin = mean_tma1 - sd_tma1, ymax = mean_tma1 + sd_tma1))
ggsave("draft_figures/Exp0879--20200914_tma_DRCs_model3_fixed_2_mean.pdf", p_tma_mean, width = 15, height = 15)
```

```{r}
p_tma_s1 <- paper1_tma_DRCs %>%
  ungroup() %>%
  filter(which_model == "s1_d_list") %>%
  # select(compound, compound_conc, tma1, tma2, xtal_hit, compound_f) %>%
  pivot_longer(cols = c(tma1, tma2)) %>%
 # filter(name == "tma1") %>%
    filter(value < 55) %>%
    filter(value > 48) %>%
  
ggplot( aes(x = compound_conc, 
            y = value,
            color = xtal_hit
            )) +
  geom_point(alpha = 0.5)+
  #ylim(c(49, 55)) +
  #geom_linerange(aes(ymin = `Tma 1`  -tma1, ymax = tma1  + tma1_sd)) +
  facet_wrap(~compound_f, scales = "fixed") +
  labs( x = "[Compound] (µM)", y = "Tma of major transtion (Model 2)", title = "Nsp3 Mac1 Fragments, Batch 1") 
  ggsave("draft_figures/Exp0879--20200914_tma_DRC_model1_fixed.pdf", p_tma, width = 15, height = 15)

```

Make violin raincloud plots for the DMSO and ADPribose tmas 
```{r}
control_tmas <- all_tmas %>% filter(compound %in% c("DMSO", "ADPribose"))
# all_model_tmas <- lapply(results_extracted, `[[`,  j = "model_tmas" ) %>%
#                   bind_rows()
# 
# control_tmas <- paper1_tmas %>%
#                 pivot_longer( c(tma1, tma2 ), names_to = "which_tma", values_to = "value") %>%
#                 filter(compound %in% c("ADPribose", "DMSO")) %>%
#                 rename(which_model = two_sig_model) %>%
#                 unite(which_exp_tma, c(plate_number, which_tma), remove = FALSE)

control_raincloud <- control_tmas %>%
  filter(which_model == "s2_list",
         # value > 46,
         # value < 75,
         compound == "DMSO") %>%
  ggplot(data = . , 
                 aes(x = plate_number, 
                     y = value, 
                     fill = plate_number, 
                     group = which_exp_tma)) +
          
          geom_flat_violin(position = position_nudge(x = .2, y = 0), 
                           alpha = .8) +
          
          geom_point(aes(color = plate_number), 
                     position = position_jitter(width = .15), 
                     size = .5, 
                     alpha = 0.8) +
  
          geom_boxplot(width = .15,  outlier.shape = 19, alpha = 0.5, coef = 1.5) +
  
          #scale_shape_manual(values = c(4,16) )+
         # scale_y_continuous( trans = "log2" ) +

          theme_bw() +
          raincloud_theme +
          labs(title = "DMSO Tmas \nOver different experiments", 
               y = "RFU (TAMRA 535/580 nm)",
               x = "Plate Number") +
          
          coord_flip() +
  
          guides(fill="none", 
                 color = "none",
                 shape = guide_legend( title = "",
                                       labels = paste("long", c(5, 10)),
                                       labels = c(`FALSE` = "Retained", `TRUE` = "Rejected"),
                                       override.aes = list(size = 5),
                                       legend.justification = c("right", "top")
                                       #legend.position = c(.95, .95)
                                       )
                 ) 
  
  
# Save one version with the experiment numbers
control_raincloud_final_exp <- control_raincloud  + scale_x_discrete( labels = control_tmas$plate_number %>% unique() %>% readr::parse_number() %>% substr(0, 3) )

# Save one version with consecutive numbers
control_raincloud_final <- control_raincloud + scale_x_discrete( labels = 23:1 )

ggsave("cleaned_analysis/Exp0879--20200913_DMSO_ADPr_Tmas_exp_numbered.pdf", control_raincloud_final_exp, width = 7, height = 4)
#ggsave("cleaned_analysis/Exp0879--20200913_starting_RFU_all_experiment_consec_numbered.pdf", g_order_num, width = 7, height = 10)
  
```

```{r}
######### Each experiment individually  ------------------
g <- RFU_25 %>%
          ggplot(data = . , 
                 aes(x = plate_number, 
                     y = value, 
                     fill = plate_number, 
                     group = plate_number)) +
          
          geom_flat_violin(position = position_nudge(x = .2, y = 0), 
                           alpha = .8) +
          
          geom_point(aes(shape = outlier,
                         color = plate_number), 
                     position = position_jitter(width = .15), 
                     size = .5, 
                     alpha = 0.8) +
  
          geom_boxplot(width = .15,  outlier.shape = 19, alpha = 0.5, coef = 1.5) +
  
          scale_shape_manual(values = c(4,16) )+
          scale_y_continuous( trans = "log2" ) +

          theme_bw() +
          raincloud_theme +
          labs(title = "Some day-to-day variation in starting RFUs\nmotivates experiment-specific threshholding", 
               y = "RFU (TAMRA 535/580 nm)",
               x = "Plate Number") +
          
          coord_flip() +
  
          guides(fill="none", 
                 color = "none",
                 shape = guide_legend( title = "",
                                       labels = paste("long", c(5, 10)),
                                       labels = c(`FALSE` = "Retained", `TRUE` = "Rejected"),
                                       override.aes = list(size = 5),
                                       legend.justification = c("right", "top")
                                       #legend.position = c(.95, .95)
                                       )
                 ) 

# Save one version with the experiment numbers
g_expnum <- g + scale_x_discrete( labels = all_TAMRA$plate_number %>% unique() %>% extract_numeric() %>% substr(0, 3) )

# Save one version with consecutive numbers
g_order_num <- g + scale_x_discrete( labels = 16:1 )

ggsave("cleaned_analysis/Exp0879--20200913_starting_RFU_all_experiment_exp_numbered.pdf", g_expnum, width = 7, height = 10)
ggsave("cleaned_analysis/Exp0879--20200913_starting_RFU_all_experiment_consec_numbered.pdf", g_order_num, width = 7, height = 10)
```

```{r}
control_tmas <- paper1_tma_DRCs %>%
                filter(compound %in% c("DMSO", "ADPribose", "ADP-ribose")) %>%
  mutate(compound, recode(compound, ADPribose = "ADP-ribose"))

paper1_tma_DRCs$compound %>% table()
```


One-way ANOVA to determine if there is a DRC for each of these variables
```{r}
# First, include the DMSO average as the zero-point for each of the compounds

```

DMSO and ADP ribose statistics
```{r}
#### Isolate the relevant data

  
  
has_compound_conc_col <-  map( dfs_protein_TAMRA , ~"compound_conc" %in% names(.x)  ) %>% as_vector() # just the channel of interest
ADPr <-  map( dfs_protein_TAMRA ,
                      ~filter(.x,  # for each tibble
                              across(any_of("compound") | any_of("ZINC"), # if there's a compound or ZINC column
                               ~.x == c("ADPribose")) )) %>% # keep ADPr
          map(. , ~mutate_all(.x, as.character)) %>%
          .[has_compound_conc_col] %>%
          map(. , ~select(.x, c(Temperature, plate_number, value, compound_conc)) ) %>%
          bind_rows() %>%
          unite("plate_compound_conc", # name of new column
                        plate_number, compound_conc, # unite these
                        remove = FALSE) %>%
          mutate_all( . ,convert_numerics) %>% # this misses the compond conc column--is it because of decimal places??
          mutate_at( . ,"compound_conc", as.numeric)

#### Calculate correlation statstics--------
ADPr_25_stats <- ADPr %>%
                filter(Temperature == 25) %>%
                group_by(plate_number) %>%
                nest() %>%
                  mutate(
                  test = map(data, ~ cor.test(.x$compound_conc, .x$value)), # S3 list-col
                  tidied = map(test, broom::tidy)) %>%
                unnest(tidied)
```

Raw data for all paper 1 compounds
```{r}
paper1_raw_data <- with_compound_col %>%
                      .[has_compound_conc_col] %>%
                      map(. , ~select(.x, c(variable, condition, plate_number, compound, compound_conc, Temperature, value, value_norm)) ) %>%
                      map(. , ~mutate_all(.x, as.character)) %>%

                  
                     bind_rows()  %>%
                    ungroup()%>%
                    mutate_all( . ,convert_numerics) %>% # this misses the compond conc column--is it because of decimal places??
                    mutate_at( . ,"compound_conc", as.numeric) %>%
   left_join(paper1_cmpds_table %>% select(compound, `xtal hit`)) %>%
  rename(xtal_hit = `xtal hit`)

paper1_raw_data %>% head()

paper1_raw_data %>%
  filter(plate_number %in% c("Exp0868", "Exp0877_plate3", "Exp0877_plate4"),
         !compound %in% c("NA", "6511", "8637", "9020")) %>% # three compounds not for this paper, and character-ized "NA"s

ggplot( aes(x = Temperature, 
            y = value_norm,
            color = compound_conc,
            group = variable
            )) +
  geom_line(alpha = 0.5, size = 0.2)+
  xlim(c(44, 60))+
  scale_color_viridis_c(trans = "log2", direction = -1) +
  #ylim(c(49, 55)) +
  #geom_linerange(aes(ymin = `Tma 1`  -tma1, ymax = tma1  + tma1_sd)) +
  facet_wrap(~compound, scales = "fixed") +
  labs( x = "Temperature (C)", y = "Normalized RFU", title = "Nsp3 Mac1 Fragments DSF data, Batch 1") -> p_raw 
  ggsave("draft_figures/Exp0879--20200914_DRC_raw.pdf", p_raw, width = 15, height = 15)

```




Determine DMSO and ADP ribose values from all experiments
```{r}
# extract DMSO and ADP ribose data only

# plot the tmas, grouped by experiment

# group based on buffer and DMSO/ADPribose and average

```

ATP and ADP barely stabilize
```{r}
# extract DMSO and ADP ribose data only

# plot the tmas, grouped by experiment

# group based on buffer and DMSO/ADPribose and average

```


Main figure: Publication-quality ADP, ATP, ADP ribose dose-response figure
```{r}
# panel 1: raw dara

# panel 2: tmas

# statistical tests 

```

SI-quality figure: Triton X-100 destabilizes the protein
```{r}
# panel 1: raw dara

# panel 2: tmas

# statistical tests 

```

SI-quality figure: Higher protein concentrations destabilize the protein
```{r}
# panel 1: raw dara

# panel 2: tmas

# statistical tests 

```

SI-quality figure: dose-response for all paper 1 compounds (60 compounds)
```{r}
# panel 1.1: raw data, for xtal hits

# panel 1.2: raw data, for non xtal hits

# panel 2.1: tmas, for xtal hits

# panel 2.2: tmas, for non xtal hits

# statistical tests: which compounds induce a significant thermal shift?
```

SI-quality figure: Comparison of xtal results and DSF results
```{r}
### Determine:
# fraction enrichment
# statistical test to say how good of a parameter this is 

# panel 1: for primary transition

# panel 2: for secondary transition

# panel 3: for initial fluorescence

# panel 4: for total fluorescence

# panel 5: for BIC

```

Main figure: dose-response for 
```{r}

```

```{r}
# isolate just the experiments which tested both ADP ribose and DMSO
# https://stackoverflow.com/questions/45146688/execute-dplyr-operation-only-if-column-exists

                 # map( . ,   ~rename( .x, compound_new = starts_with("ZINC"))) 
                 # map( . , ~select( .x, -one_of("compound")))
```


Ultimately, move this to hit calling criteria exploration notebook
Does ADP ribose consistently decrease the starting RFU?
```{r}
###### DO NOT DELETE THIS!!!! ######
#### Isolate the relevant data
has_compound_conc_col <-  map( dfs_protein_TAMRA , ~"compound_conc" %in% names(.x)  ) %>% as_vector() # just the channel of interest
ADPr <-  map( dfs_protein_TAMRA ,
                      ~filter(.x,  # for each tibble
                              across(any_of("compound") | any_of("ZINC"), # if there's a compound or ZINC column
                               ~.x == c("ADPribose")) )) %>% # keep ADPr
          map(. , ~mutate_all(.x, as.character)) %>%
          .[has_compound_conc_col] %>%
          map(. , ~select(.x, c(Temperature, plate_number, value, compound_conc)) ) %>%
          bind_rows() %>%
          unite("plate_compound_conc", # name of new column
                        plate_number, compound_conc, # unite these
                        remove = FALSE) %>%
          mutate_all( . ,convert_numerics) %>% # this misses the compond conc column--is it because of decimal places??
          mutate_at( . ,"compound_conc", as.numeric)

#### Calculate correlation statstics--------
ADPr_25_stats <- ADPr %>%
                filter(Temperature == 25) %>%
                group_by(plate_number) %>%
                nest() %>%
                  mutate(
                  test = map(data, ~ cor.test(.x$compound_conc, .x$value)), # S3 list-col
                  tidied = map(test, broom::tidy)) %>%
                unnest(tidied)

##### Make the facet plat ---------
experiment_labs <- paste0("Experiment ", 1:10)
names(experiment_labs) <- ADPr$plate_number %>% unique()

experiment_labs

ADPr_vs_starting_val <- ADPr %>%
  filter(Temperature == 25,
         !plate_number %in% c("Exp0866_plate1", "Exp0866_plate2")) %>%
                          ggplot(aes(x = compound_conc, y = value)) +
                          geom_jitter( aes(group = plate_compound_conc), alpha = 0.5) +
                           scale_x_continuous(trans = "log2", breaks = c(0, 10, 100,1000))  +
                           facet_wrap(~plate_number,
                                      labeller = labeller(plate_number = experiment_labs),
                                      ncol = 4) +
                            theme_bw() +
  geom_boxplot(aes(group = plate_compound_conc), width = 1,  outlier.shape = NA, alpha = 0.5) +
  geom_text(data = ADPr_25_stats %>% 
                  filter(!plate_number %in% c("Exp0866_plate1", "Exp0866_plate2")), 
            aes(x = 7, y = 8700, label = paste0("p = ", p.value %>% round(2)))) +
  raincloud_theme +
  theme(axis.text.x = element_text(angle = 90)) +
  ylim(c(0, 10050))+
  labs(title = "Initial RFU not correlated with [ADP ribose]\nAcross 8 independent experiments\n(Pearson's Correllation Coefficient> 0.05)",
       y = "RFU (TAMRA, 535/580 nm)",
       x = "[ADP ribose] (µM)") 


ggsave("cleaned_analysis/Exp0879--20200913_starting_RFU_ADPr_not_correlated.pdf", ADPr_vs_starting_val, width = 7, height = 4)
```
