---
title: "Assembling Fragment data"
output: html_notebook
---

This notebook contains work done to assemble data from Nsp3 fragment test and all associated experiments for the first paper.
Analysis

```{r}
library(quantmod) # contains the findValleys function, which maybe we should just extract and put verbatim in a source file instead of loading this whole thing...?
library(minpack.lm) # contains the nlsLM function, which we use for our fitting
library(modelr) # used in both the data modeling and the analysis model fitting 
library(SciViews) # contains the ln function used in the data modeling
library(signal) # contains the savistky golay filter (savgolfilt), used to generate the first derivative data in both data modeling and analysis model fitting  
library(ggrepel) # for plot labeling
library(tidyverse)
source("scripts/analysis.R")
source("scripts/plotting.R")
source("scripts/screen_analysis.R")
filter <- dplyr::filter # filter is masked from dplyr by signal
as_vector <- purrr::as_vector
```

```{r}

convert_numerics <- function( vec ) {
    
    if(all(varhandle::check.numeric(vec))){
        # convert the vector to numeric
        vec <- as.numeric(vec)
    }
    vec
}

find_tmas_879 <- function(by_variable_raw, 
                      low_T = 25,
                      high_T = 94,
                      n_meas = 69,
                      filter_criteria) {
  # get the filtering and smoothing parameters
  n2r <- make_temp_n2r(range(low_T:high_T)) 
  win3d <- floor(3/((n2r(1) - n2r(0))/n_meas))
  if ( win3d < 5 ) { win3d <<- 5 }
  
  peak_finder_nest <<- make_peak_finder_nest( win3d )
  # sgfilt_nest <- sgfilt_set_n(n_ = find_sgolay_width( win3d ))
  
  sgfilt_nest <- sgfilt_set_n(n_ = 13)
  
  # fit only the channels which have signal
  by_variable <- by_variable_raw
  
  
  df_tms <- by_variable %>% #df_int %>% # add the first derivative Tms
    plyr::mutate(sgd1 = purrr::map(data, sgfilt_nest, m_ = 1)) %>% # add the first derivative data
    plyr::mutate(dRFU_tma = as_vector(purrr::map2(data, sgd1, Tm_by_dRFU))) # find the dRFU tmas
  
  # fit to all models        
  start_pars <- get_start_pars(by_variable)
  s1_list <- model_all(s1_model, "s1_pred", start_pars, win3d) # requires "well" and "condition" columns
  s1_d_list <- model_all(s1_d_model, "s1_d_pred", start_pars, win3d)
  s2_list <- model_all(s2_model, "s2_pred", start_pars, win3d)
  s2_d_list <- model_all(s2_d_model, "s2_d_pred", start_pars, win3d)
  
  save_list <- list(by_variable = by_variable,
                    df_tms = df_tms,
                    start_pars = start_pars,
                    s1_list = s1_list,
                    s1_d_list = s1_d_list,
                    s2_list = s2_list,
                    s2_d_list = s2_d_list)
}

```

```{r}
process_screen_879 <- function(df_raw,
                           save_path = "") {
  
                              low_T <- 25
                              high_T <- 94
                              n_meas <- 69
                              ignore_vars <- ""
                              fit_if <- c("TAMRA")
                              save_fits <- TRUE
                              save_name <- "fits.rds"
                              temp_range <- c(25, 85)
                              quick_look <- TRUE
                              
                              by_variable <- df_raw %>%
                              nest(data = c(Temperature, value, channel, Temperature_norm, value_norm))
                            
                            fits <- find_tmas_879(by_variable_raw = by_variable,
                                              low_T = low_T,
                                              high_T = high_T,
                                              n_meas = 69)  #### THIS NEEDS TO BE FIXED! Sometimes throws an error in sgolayfilt odd requirement if set dynamically #df_raw$Temperature %>% unique() %>% length(),
                          
                            outlist <- list(df_raw = df_raw,
                                            by_variable = by_variable,
                                            fits = fits)
                          
                          
                            if (save_fits != FALSE) { paste0(save_path, save_name)  %>% write_rds( . , x = outlist) }
                            print(save_path)
                            outlist
                            
                          }

```

Read in formatted data from all processed experiments
```{r}
# The folder names holding the files to be read are given manually
  exp_info <- readxl::read_excel("Exp0879--20200912_fragment_exp_to_process.xlsx") # organizer of the experiments to be processed in this experiment
  
  exp_folders <- exp_info$`Exp title` %>%  
                 paste0( "~/Box Sync/data/", . , "/for_Exp0879") 
  
# Extract the correct file names from these folders by regex in the file name
  # Full directories
  rds_files <- lapply( exp_folders, dir, full.names = T, pattern = "processed_for_Exp0879.rds") %>%   # extract names of all fiels to be read
               flatten()  %>% 
               as_vector()
  
  # Unique filename components
  rds_names <- lapply( exp_folders, dir, full.names = F, pattern = "processed_for_Exp0879.rds") %>%   # remove .rds names, to use as list names for the experiments
               flatten() %>%
                as_vector() %>%
               gsub(x = . , pattern = "--processed_for_Exp0879.rds", replacement = "")

# Read all RDSs from directories
  dfs_list <- lapply(rds_files, readRDS) # read in all pre-processed experiments

# Name the list elements
  names(dfs_list) <-  rds_names # set the ist element names as the experiment

dfs_protein_EBPS <- map(dfs_list, ~filter(.x, protein %in% c("SP0148", "SP0150", "Buffer")) ) # remove any empty wells (in this script, this should already be done)

# Isolate just the data relevant for analysis
dfs_protein_TAMRA <- map(dfs_protein_EBPS, ~filter(.x, protein %in% c("SP0148", "SP0150")) ) %>% 
                      map( . , ~filter(.x, channel_f == "TAMRA") ) %>% # just the channel of interest
                      map( . , ~filter(.x, protein != "Buffer") ) # just the protein-containing wells
 
  # Save the full list of read RDSs
  write_rds(x = dfs_protein_EBPS, "analyzed/Exp0879--20200912_all_dfs_list_no_empties.rds") # write this list to an rds in this directory ## THIS IS TOO LARGE TO UPLOAD TO GITHUB!!!!
  write_rds(x = dfs_protein_TAMRA, "analyzed/Exp0879--20200912_all_dfs_as_input_to_analysis.rds") # write this list to an rds in this directory ## THIS IS TOO LARGE TO UPLOAD TO GITHUB!!!!
  
```

Analyze
```{r}
all_processed <- map2(dfs_protein_TAMRA, 
                      dfs_protein_TAMRA %>% names() %>% paste0("analyzed/", . , "_tma_analysis_results_"),
                      process_screen_879)
```

Highlighting poor fits/odd curves
```{r}
#install.packages("PupillometryR")
# library(PupillometryR)

# library(readr)
# library(tidyr)
# library(ggplot2)
library(Hmisc)
# library(plyr)
# library(RColorBrewer)
library(reshape2)

mini_test <- dfs_protein_TAMRA$Exp0827


all_TAMRA <- dfs_protein_TAMRA %>%
              map(. , ~select(.x, c(Temperature, plate_number, value, value_norm)) ) %>%
            map(. , ~filter(.x, dye != "T004") ) %>%
              bind_rows()

all_25 <- all_TAMRA %>%
           filter(Temperature == 25) 
# borrowed from Paula Andrea Martinez's post mentioned above
g <- 
  ggplot(data = all_25, 
         aes(x = plate_number, 
             y = value, 
             fill = plate_number)) +
  geom_flat_violin(position = position_nudge(x = .2, y = 0), alpha = .8) +
  geom_point(aes(y = value, color = plate_number), 
             position = position_jitter(width = .15), size = .5, alpha = 0.8) +
  ylim(c(0, max(all_25$value))) +
  scale_y_continuous(trans = "log2")
  # geom_point(data = mini_test, aes(x = plate_number, y = mean), 
  #            position = position_nudge(x = 0.3), size = 2.5) +
  # geom_errorbar(data = mini_test, aes(ymin = lower, ymax = upper, y = mean), 
  #               position = position_nudge(x = 0.3), width = 0) +
  # expand_limits(x = 5.25) +
  # guides(fill = FALSE) +
  # guides(color = FALSE) +
  # coord_flip() + 
  # scale_color_brewer(palette = "Spectral") +
  # scale_fill_brewer(palette = "Spectral") +
  # theme_bw() 

g
# +
#   raincloud_theme
                         
                         my_datal <- melt(my_data, id.vars = c("Participant"), measure.vars = c("AngerUH", "DisgustUH", "FearUH", "HappyUH"), variable.name = "EmotionCondition", value.name = "Sensitivity")

# call out by the starting RFU in the raw data
mini_test %>%
  filter(Temperature == 25) %>%
  ggplot() +
  PupillometryR::geom_flat_violin() 
 # geom_density(aes(value))

# call out by the residuals in the fits

```


Post analysis cleaning
```{r}
# take one screening list

# take binnned mean of Tma 1 and Tma 2

# re-assign Tma1 and Tma2 based on whichever one a Tma is closer to 

```


Make files necessary to isolate paper 1-relevant experiments
```{r}
# mapping ZINCid to 4-digit tube label
# % triton by experiment
```


Determine DMSO and ADP ribose values from all experiments
```{r}
# extract DMSO and ADP ribose data only

# plot the tmas, grouped by experiment

# group based on buffer and DMSO/ADPribose and average

```

ATP and ADP barely stabilize
```{r}
# extract DMSO and ADP ribose data only

# plot the tmas, grouped by experiment

# group based on buffer and DMSO/ADPribose and average

```


Main figure: Publication-quality ADP, ATP, ADP ribose dose-response figure
```{r}
# panel 1: raw dara

# panel 2: tmas

# statistical tests 

```

SI-quality figure: Triton X-100 destabilizes the protein
```{r}
# panel 1: raw dara

# panel 2: tmas

# statistical tests 

```

SI-quality figure: Higher protein concentrations destabilize the protein
```{r}
# panel 1: raw dara

# panel 2: tmas

# statistical tests 

```

SI-quality figure: dose-response for all paper 1 compounds (60 compounds)
```{r}
# panel 1.1: raw data, for xtal hits

# panel 1.2: raw data, for non xtal hits

# panel 2.1: tmas, for xtal hits

# panel 2.2: tmas, for non xtal hits

# statistical tests: which compounds induce a significant thermal shift?
```

SI-quality figure: Comparison of xtal results and DSF results
```{r}
### Determine:
# fraction enrichment
# statistical test to say how good of a parameter this is 

# panel 1: for primary transition

# panel 2: for secondary transition

# panel 3: for initial fluorescence

# panel 4: for total fluorescence

# panel 5: for BIC

```

Main figure: dose-response for 
```{r}

```















