---
title: "R Notebook"
output: html_notebook
---

```{r}

```


Highlighting poor fits/odd curves
```{r}
#install.packages("PupillometryR")
# library(PupillometryR)

# library(readr)
# library(tidyr)
# library(ggplot2)
library(Hmisc)
# library(plyr)
# library(RColorBrewer)
library(reshape2)

mini_test <- dfs_protein_TAMRA$Exp0827


all_TAMRA <- dfs_protein_TAMRA %>%
              map(. , ~select(.x, c(Temperature, plate_number, value, value_norm)) ) %>%
            map(. , ~filter(.x, dye != "T004") ) %>%
              bind_rows()

all_25 <- all_TAMRA %>%
           filter(Temperature == 25) 
# borrowed from Paula Andrea Martinez's post mentioned above
g <- 
  ggplot(data = all_25, 
         aes(x = plate_number, 
             y = value, 
             fill = plate_number)) +
  geom_flat_violin(position = position_nudge(x = .2, y = 0), alpha = .8) +
  geom_point(aes(y = value, color = plate_number), 
             position = position_jitter(width = .15), size = .5, alpha = 0.8) +
  ylim(c(0, max(all_25$value))) +
  scale_y_continuous(trans = "log2")
  # geom_point(data = mini_test, aes(x = plate_number, y = mean), 
  #            position = position_nudge(x = 0.3), size = 2.5) +
  # geom_errorbar(data = mini_test, aes(ymin = lower, ymax = upper, y = mean), 
  #               position = position_nudge(x = 0.3), width = 0) +
  # expand_limits(x = 5.25) +
  # guides(fill = FALSE) +
  # guides(color = FALSE) +
  # coord_flip() + 
  # scale_color_brewer(palette = "Spectral") +
  # scale_fill_brewer(palette = "Spectral") +
  # theme_bw() 

g
# +
#   raincloud_theme
                         
                         my_datal <- melt(my_data, id.vars = c("Participant"), measure.vars = c("AngerUH", "DisgustUH", "FearUH", "HappyUH"), variable.name = "EmotionCondition", value.name = "Sensitivity")

# call out by the starting RFU in the raw data
mini_test %>%
  filter(Temperature == 25) %>%
  ggplot() +
  PupillometryR::geom_flat_violin() 
 # geom_density(aes(value))

# call out by the residuals in the fits

```


Post analysis cleaning
```{r}
# take one screening list

# take binnned mean of Tma 1 and Tma 2

# re-assign Tma1 and Tma2 based on whichever one a Tma is closer to 

```


Make files necessary to isolate paper 1-relevant experiments
```{r}
# mapping ZINCid to 4-digit tube label
# % triton by experiment
```


Determine DMSO and ADP ribose values from all experiments
```{r}
# extract DMSO and ADP ribose data only

# plot the tmas, grouped by experiment

# group based on buffer and DMSO/ADPribose and average

```

ATP and ADP barely stabilize
```{r}
# extract DMSO and ADP ribose data only

# plot the tmas, grouped by experiment

# group based on buffer and DMSO/ADPribose and average

```


Main figure: Publication-quality ADP, ATP, ADP ribose dose-response figure
```{r}
# panel 1: raw dara

# panel 2: tmas

# statistical tests 

```

SI-quality figure: Triton X-100 destabilizes the protein
```{r}
# panel 1: raw dara

# panel 2: tmas

# statistical tests 

```

SI-quality figure: Higher protein concentrations destabilize the protein
```{r}
# panel 1: raw dara

# panel 2: tmas

# statistical tests 

```

SI-quality figure: dose-response for all paper 1 compounds (60 compounds)
```{r}
# panel 1.1: raw data, for xtal hits

# panel 1.2: raw data, for non xtal hits

# panel 2.1: tmas, for xtal hits

# panel 2.2: tmas, for non xtal hits

# statistical tests: which compounds induce a significant thermal shift?
```

SI-quality figure: Comparison of xtal results and DSF results
```{r}
### Determine:
# fraction enrichment
# statistical test to say how good of a parameter this is 

# panel 1: for primary transition

# panel 2: for secondary transition

# panel 3: for initial fluorescence

# panel 4: for total fluorescence

# panel 5: for BIC

```

Main figure: dose-response for 
```{r}

```
